---
title: "Assignment 1 Task 4 Toolik Weather"
author: "Michelle Geldin"
date: "10/9/2021"
output: html_document
---
## Overview

The ‘toolik_daily_weather.csv’ data contains daily meteorological data (air temperature, windspeed, precipitation, etc.) recorded at Toolik Station, Alaska.

### Data Citation

Shaver, G. 2019. A multi-year DAILY weather file for the Toolik Field Station at Toolik Lake, AK starting 1988 to present. ver 4. Environmental Data Initiative. https://doi.org/10.6073/pasta/ce0f300cdf87ec002909012abefd9c5c

## Setup
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

## Read in the Data

```{r}
toolik_weather <- read_csv(here("data", "toolik_daily_weather.csv"))
```

## Data Wrangling

```{r}
toolik_weather_clean <- toolik_weather %>%
  clean_names() %>%
  select(year, date, daily_air_temp_mean_c, daily_air_temp_abs_max_c, daily_air_temp_abs_min_c) %>%
  filter(year >= 2010)
```

## Data Visualization

```{r}
ggplot(data = toolik_weather_clean, aes(x = date, y = daily_air_temp_mean_c)) +
  geom_line() +
  theme_bw() +
  labs(x = "Date Geldin", y = "Daily Air Temperature (Celsius) Geldin", title = "Daily Air Temperature (Celsius) by Date Geldin")
```

## End Task