---
title: "Task 1 - Global sea level rise due to glacial melt"
author: "Michelle Geldin"
date: "10/6/2021"
output: html_document
---
## Overview
This code wrangles and visualizes global glacial volume loss from 1961 - 2003 using curated data (glacial_loss.csv) from the National Snow and Ice Center (http://nsidc.org/data/g10002.html)

### Data Citation
Dyurgerov, M. Edited by M. Meier and R. Armstrong. 2002, updated 2005. Glacier Mass Balance and Regime Measurements and Analysis, 1945-2003, Version 1. Boulder, Colorado USA. NSIDC: National Snow and Ice Data Center. doi: https://doi.org/10.7265/N52N506F.


## Setup
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(ggplot2)
```

## Read in the Data

```{r}
glacial_loss <- read_csv(here("data_task_1", "glacial_loss.csv")) %>%
  clean_names()
```
## Data Wrangling

```{r}
glacial_data <- glacial_loss %>%
  select(year, cumulative_sea_level_rise)
```

## Data Visualization

```{r}
ggplot(data = glacial_data, aes(x = year, y = cumulative_sea_level_rise)) +
  geom_jitter()
  theme_dark()
  labs(x = "year geldin",
       y = "cumulative sea level rise geldin",
       title = "cumulative sea level rise per year geldin")
```
## End Task
