---
title: "Assignment 1 Task 3 Penguins"
author: "Michelle Geldin"
date: "10/9/2021"
output: html_document
---
## Overview

The ‘penguins.csv’ data contains body size measurements for three different species of penguins (Adélie, Chinstrap, and Gentoo) recorded by Gorman et al. on islands near Palmer Archipelago, Antarctica, from 2007 - 2009.

### Data Citation

Gorman KB, Williams TD, Fraser WR (2014). Ecological sexual dimorphism and environmental variability within a community of Antarctic penguins (genus Pygoscelis). PLoS ONE 9(3):e90081. https://doi.org/10.1371/journal.pone.0090081

## Setup
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```
## Read in the Data

```{r}
penguin_data <- read_csv(here("data", "penguins.csv"))
```
## Data Visualization

```{r}
ggplot(data = penguin_data, aes(x = bill_depth_mm, y = bill_length_mm)) +
  geom_point(aes(color = species)) +
  theme_minimal() +
  labs(x = "Penguin Bill Depth (mm) Geldin", y = "Penguin Bill Length (mm) Geldin", title = "Penguin Bill Depth Compared to Penguin Bill Length")
```

```{r}
ggplot(data = penguin_data, aes(x = flipper_length_mm, y = species)) +
  geom_jitter(width = 0.2) +
  theme_minimal() +
  labs(x = "Penguin Flipper Length (mm) Geldin", y = "Penguin Species Geldin", title = "Penguin Flipper Length by Species Geldin")
```
## Data Wrangling

```{r}
gentoo_penguins <- penguin_data %>%
  filter(species == "Gentoo")
```

## More Data Visualization

```{r}
ggplot(data = gentoo_penguins, aes(x = body_mass_g)) +
  geom_histogram(color = "white", fill = "burlywood1") +
  theme_minimal() + 
  labs(x = "Gentoo Penguin Body Mass (g) Geldin", y = "Number of Gentoo Penguins", title = "Gentoo Penguins per Body Mass (g) Geldin")
```

## End Task

